---
title: "Sample RMarkdown Document"
author: "Adam Kaplan"
output: pdf_document
date: "2023-09-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(foreign)
```

# Basics
Here is my sample `rmarkdown` document. You can write in Markdown, while adding in executable `R` code:
```{r}
x <- 2 + 2
```

Or non-executable code:
```{r}
y <- 2 + 3
```

As well as LaTeX chunks:

$$
\begin{aligned}
 Y_i &= \alpha + \beta x_i + \varepsilon_i  \\
 Y_i - \varepsilon_i &= \alpha + \beta x_i  \\
\end{aligned} 
$$

# `R` and LaTeX in RMarkdown

The powerful part of RMarkdown is that you can include R outputs, such as plots or tables directly without having to mess around with LaTeX code.

## Plots
```{r pressure}
head(cars)
plot(pressure)
```

## Tables

```{r, results = 'asis'}
# we will use mtcars dataset already in R

our_table <- mtcars %>% 
  group_by(cyl) %>%
  summarize(mean_mpg = mean(mpg))

library(xtable)
print(xtable(our_table))

print(xtable(our_table),
       file = "./our_table.tex")
```

```{r, results = 'asis'}
our_reg <- lm(cyl ~ mpg, data = mtcars)

library(stargazer)
stargazer(our_reg,
          header = FALSE)

stargazer(our_reg, 
          header = FALSE,
          out = "./our_reg.tex")
```


# Acknowledgements

I assemble this document from multiple other introductory RMarkdown documents written by Elizabeth Parker-Magyar.
